Ms 1

### 2018-01-09 ms1/ms1_display.Rmd
major cleanups

```{r pop_chars}
pop_chars = read_tsv('tables/pop_chars.tsv') %>%
  mutate_at(vars(n_female:n_region_midwest), function(x) x / .$n_bene * 100)

@@

pop_char_trends = pop_chars %>%
  select(year, n_bene, mean_age, mean_n_cc, n_female:n_region_midwest) %>%
  gather('key', 'value', -year) %>%
  arrange(key, year) %>%
  group_by(key) %>%
  summarize(p=trend_p(value)) %>%
  mutate(adj.p=p.adjust(p, method='BH'))

pop_chars %>%
  mutate(n_bene=prettyNum(n_bene, big.mark=',')) %>%
  mutate_at(vars(mean_age, sd_age, n_female:n_region_midwest), function(x) format(x, digits=1, nsmall=1)) %>%
  mutate_at(vars(mean_n_cc, sd_n_cc), function(x) format(x, digits=2, nsmall=2)) %>%
  gather('key', 'value', -year) %>%
  spread(year, value) %>%
  mutate(key=factor(key, levels=names(pop_chars))) %>%
  arrange(key) %>%
  kable(caption='Population characteristics')

pop_char_trends %>%
  kable(caption='Trends in population characteristics')
```

@@

```{r claims_by_fill}
claims_by_fill = read_tsv('tables/claims_by_fill.tsv') %>%
  mutate(f_refill=refills/overall_wrefill)

claims_by_fill %>%
  mutate_at(vars(-f_refill), function(x) prettyNum(x, big.mark=',')) %>%
  kable(caption='PDEs by refill')
```

@@

```{r raw_drug_trends}
claims_by_abx = read_tsv('tables/claims_by_abx.tsv') %>%
  mutate(abx=fct_inorder(factor(abx)))

claims_by_abx %>%
  mutate(cpkp=round(cpkp)) %>%
  spread(year, cpkp) %>%
  kable(caption='Raw drug CPKP')
```

```{r raw_drug_trends_figure}
abx_levels = levels(claims_by_abx$abx)

claims_by_abx %>%
  filter(abx %in% c('overall', 'overall_approp', 'overall_inapprop')) %>%
  ggplot(aes(x=year, y=cpkp, color=abx)) +
  geom_line() +
  scale_y_continuous(limits=c(0, 1400), breaks=c(0, 250, 500, 750, 1000, 1250, 1400)) +
  coord_fixed(ratio=4/1400*1.25) +
  theme_minimal() +
  theme(panel.grid.minor.x=element_blank()) +
  ggtitle('Unadjusted consumption, all abx')

@@

```{r drug_trends}
est2pct = function(x) (exp(x) - 1)*100

drug_trends = read_tsv('tables/trend_models.tsv') %>%
  filter(term=='year') %>%
  arrange(estimate) %>%
  mutate(estimate=3*estimate,
         std.error=sqrt(3)*std.error) %>%
  mutate(ci=1.96*std.error,
         ci_lo=estimate-ci,
         ci_hi=estimate+ci) %>%
  mutate(y=est2pct(estimate),
         ymin=est2pct(ci_lo),
         ymax=est2pct(ci_hi)) %>%
  mutate(change=sprintf('%.2f (%.2f -- %.2f)', y, ymin, ymax))
```

```{r drug_trends_display}
format_p = function(p) {
  if_else(p < 0.001, '< 0.001', as.character(round(p, 3)))
}

drug_trends %>%
  filter(abx != 'overall_wrefill') %>%
  mutate(adj.p=p.adjust(p.value, method='BH')) %>%
  select(abx, y, ymin, ymax, p.value) %>%
  mutate_at(vars(y, ymin, ymax), function(x) format(x, digits=2, nsmall=2)) %>%
  mutate(p.value=format_p(p.value)) %>%
  kable(caption='Drug trends: Percent change from 2011 to 2014')

drug_trends %>%
  filter(abx != 'overall_wrefill') %>%
  # put the abx in order
  arrange(desc(y)) %>%
  mutate(abx=fct_inorder(factor(abx))) %>%
  mutate(abx=fct_relevel(abx, c('overall', 'overall_inapprop', 'overall_approp'))) %>%
  mutate(abx=fct_rev(abx)) %>%
  # plot
  ggplot(aes(x=abx, y=y, ymin=ymin, ymax=ymax)) +
  geom_bar(stat='identity', fill='white', color='black') +
  geom_errorbar(width=0.5) +
  coord_flip() +
  xlab('') +
  ylab('adjusted change in consumption 2011 to 2014 (%)') +
  scale_y_continuous(limits=c(-22, 32.5), breaks=c(-20, -10, 0, 10, 20, 30)) +
  theme_minimal() +
  theme(axis.title.x = element_text(size=16),
        axis.text = element_text(size=16))
```

@@

```{r inappropriate_fraction}
claims_by_abx %>%
  spread(abx, cpkp) %>%
  mutate(pct_inapprop = overall_inapprop / overall * 100) %>%
  select(year, pct_inapprop) %>%
  kable(caption='Raw fraction of inappropriate prescribing')
```

@@

```{r prescribing_practice}
dx_to_pde_table = read_tsv('tables/dx_to_pde_table.tsv') %>%
  select(-n_encounters) %>%
  filter(year %in% c(2011, 2014)) %>%
  gather('abx', 'f_with_abx', azithromycin:clindamycin)

# swo: convert ORs to RRs!
risk_ratio_f = function(or, p) or / (1 + p * (or - 1))
rr2pct = function(x) (x - 1) * 100

dx_to_pde_trends = read_tsv('tables/dx_to_pde_trends.tsv') %>%
  filter(term=='year') %>%
  mutate(estimate=3*estimate,
         std.error=sqrt(3)*std.error) %>%
  mutate(ci=1.96*std.error,
         ci_lo=estimate-ci,
         ci_hi=estimate+ci) %>%
  mutate(or=   exp(estimate),
         or_lo=exp(ci_lo),
         or_hi=exp(ci_hi)) %>%
  left_join(filter(dx_to_pde_table, year==2011), by=c('dx_cat', 'abx')) %>%
  mutate(rr=   risk_ratio_f(or,    f_with_abx),
         rr_lo=risk_ratio_f(or_lo, f_with_abx),
         rr_hi=risk_ratio_f(or_hi, f_with_abx)) %>%
  mutate(y=rr2pct(rr),
         ymin=rr2pct(rr_lo),
         ymax=rr2pct(rr_hi)) %>%
  mutate(change=sprintf('%.2f (%.2f -- %.2f)', y, ymin, ymax)) %>%
  select(dx_cat, abx, change, p.value)
```

```{r combined_table}
format_pct = function(x) format(round(x*100, 2), digits=2, nsmall=2)

combined_table = dx_to_pde_table %>%
  mutate(f_with_abx=format_pct(f_with_abx)) %>%
  spread(year, f_with_abx) %>%
  left_join(dx_to_pde_trends, by=c('dx_cat', 'abx')) %>%
  mutate(p.value=format_p(p.value)) %>%
  arrange(dx_cat, abx)
```

@@

```{r respiratory}
combined_table %>%
  filter(dx_cat %in% c('pneumonia', 'sinusitis', 'uri', 'bronchitis'),
         abx %in% c('dx', 'azithromycin', 'levofloxacin', 'amoxclav')) %>%
  kable
```

@@

```{r claims_by_demography}
claims_by = function(by) {
  read_tsv(str_interp("tables/claims_by_${by}.tsv")) %>%
    mutate(group_type=by) %>%
    rename(group=!!rlang::sym(by)) %>%
    filter(year %in% c(2011, 2014)) %>%
    select(group_type, group, year, cpkp) %>%
    spread(year, cpkp) %>%
    mutate_at(vars(`2011`, `2014`), round)
}

trends_by_demography = read_tsv('tables/demography_models.tsv') %>%
  filter(term=='year') %>%
  mutate(estimate=3*estimate,
         std.error=sqrt(3)*std.error) %>%
  mutate(ci=1.96*std.error,
         ci_lo=estimate-ci,
         ci_hi=estimate+ci) %>%
  mutate(y=est2pct(estimate),
         ymin=est2pct(ci_lo),
         ymax=est2pct(ci_hi)) %>%
  mutate(change=sprintf('%.2f (%.2f -- %.2f)', y, ymin, ymax)) %>%
  select(group_type, group, change, p.value)

# overall trend row
overall_change = drug_trends %>% filter(abx=='overall') %>% pull(change)
overall_row = claims_by_abx %>%
  filter(abx=='overall', year %in% c(2011, 2014)) %>%
  mutate(cpkp=round(cpkp)) %>%
  spread(year, cpkp) %>%
  mutate(group_type='overall', group='overall', change=overall_change) %>%
  select(group_type, group, `2011`, `2014`, change)

bind_rows(
  claims_by('age_group'),
  claims_by('sex'),
  claims_by('race'),
  claims_by('region')
) %>%
  left_join(trends_by_demography, by=c('group', 'group_type')) %>%
  bind_rows(overall_row, .) %>%
  kable
```

@@

```{r other_respiratory}
combined_table %>%
  filter(dx_cat %in% c('pharyngitis', 'asthma', 'other_resp'),
         abx %in% c('azithromycin', 'levofloxacin', 'amoxclav')) %>%
  kable
```

@@

```{r uti}
combined_table %>%
  filter(dx_cat %in% c('uti', 'uti_t3'),
         abx %in% c('dx', 'ciprofloxacin', 'tmpsmx', 'nitrofurantoin')) %>%
  kable
```

@@

```{r ssti}
combined_table %>%
  filter(dx_cat %in% c('ssti', 'ssti_t3'),
         abx %in% c('dx', 'cephalexin', 'tmpsmx', 'clindamycin')) %>%
  kable
```

>>>>

```{r pop_chars}
pop_chars = read_tsv('tables/new/study_pop_chars.tsv')

pop_chars = read_tsv('tables/new/study_pop_chars.tsv') %>%
  spread(key, value) %>%
  (function (df) {
    ns1 = names(df)
    ns2 = str_replace(ns1, '^n_(?!bene|cc)', 'pct_')
    rename(df, !!!setNames(as.list(ns1), ns2))
  }) %>%
  mutate_at(vars(matches('^pct_')), function(x) x / .$n_bene * 100) %>%
  gather('key', 'value', -year)

pop_chars %>%
  mutate(key=factor(key, levels=c('n_bene', 'mean_age', 'sd_age', 'n_cc', 'sd_cc', 'pct_female', 'pct_white', 'pct_dual', 'pct_south', 'pct_midwest', 'pct_west', 'pct_northeast'))) %>%
  mutate(value=case_when(
    .$key == 'n_bene' ~ prettyNum(.$value, big.mark=','),
    .$key %in% c('n_cc', 'sd_cc') ~ format(.$value, digits=2, nsmall=2, scientific=FALSE),
    TRUE ~ format(.$value, digits=2, nsmall=1, scientific=FALSE)
  )) %>%
  spread(year, value) %>%
  kable(caption='Population characteristics')

@@

pop_chars %>%
  arrange(key, year) %>%
  group_by(key) %>%
  summarize(p_value=trend_p(value)) %>%
  kable(caption='Trends in population characteristics')
```

@@

@@

```{r raw_drug_trends_table}
claims_by_abx = read_tsv('tables/new/claims_by_abx.tsv') %>%
  gather('abx', 'n', c(-year, -bene)) %>%
  mutate(cpkp=n/bene*1000)

claims_by_abx %>%
  mutate(cpkp=round(cpkp)) %>%
  select(year, abx, cpkp) %>%
  spread(year, cpkp) %>%
  arrange(desc(`2011`)) %>%
  kable(caption='Raw drug CPKP')
```

```{r raw_drug_trends}
abx_levels = levels(claims_by_abx$abx)

claims_by_abx %>%
  filter(abx %in% c('pde', 'pde_approp', 'pde_inapprop', 'pde_nodx')) %>%
  ggplot(aes(x=year, y=cpkp, color=abx)) +
  geom_line() +
  scale_y_continuous(limits=c(0, 1400), breaks=c(0, 250, 500, 750, 1000, 1250, 1400)) +
  coord_fixed(ratio=4/1400*1.25) +
  theme_minimal() +
  theme(panel.grid.minor.x=element_blank()) +
  ggtitle('Unadjusted consumption, all abx')

@@

```{r drug_trends}
est2pct = function(x) (x - 1)*100

drug_trends = read_tsv('tables/new/abx_models.tsv') %>%
  mutate_at(vars(estimate, lower_ci, upper_ci), est2pct) %>%
  mutate(change=sprintf('%.1f (%.1f -- %.1f)', estimate, lower_ci, upper_ci))

drug_trends %>%
  mutate_at(vars(estimate, lower_ci, upper_ci), function(x) format(x, digits=1, nsmall=1, scientific=FALSE)) %>%
  kable(caption='Drug trends: Percent change from 2011 to 2014')

drug_trends %>%
  # put the abx in order
  arrange(desc(estimate)) %>%
  mutate(antibiotic=fct_inorder(factor(antibiotic))) %>%
  mutate(antibiotic=fct_relevel(antibiotic, c('n_pde', 'n_pde_approp', 'n_pde_inapprop', 'n_pde_nodx'))) %>%
  mutate(antibiotic=fct_rev(antibiotic)) %>%
  # plot
  ggplot(aes(x=antibiotic, y=estimate, ymin=lower_ci, ymax=upper_ci)) +
  geom_bar(stat='identity', fill='white', color='black') +
  geom_errorbar(width=0.5) +
  coord_flip() +
  xlab('') +
  ylab('adjusted change in consumption 2011 to 2014 (%)') +
  scale_y_continuous(limits=c(-22, 32.5), breaks=c(-20, -10, 0, 10, 20, 30)) +
  theme_minimal() +
  theme(axis.title.x = element_text(size=16),
        axis.text = element_text(size=16))
```

@@

```{r inappropriate_fraction}
claims_by_abx %>%
  filter(str_detect(abx, '^pde')) %>%
  select(year, abx, n) %>%
  spread(abx, n) %>%
  mutate_at(vars(matches('^pde_')), function(x) round(x / .$pde * 100, 1)) %>%
  select(-pde) %>%
  kable(caption='Proportion of app., inapp., and no-dx prescribing')
```

@@

```{r top_dx}
denom = claims_by_abx %>%
  select(year, bene) %>%
  distinct()

rxdx_table = read_tsv('tables/new/rxdx_counts.tsv') %>%
  left_join(denom, by='year') %>%
  mutate(cpkp=n_pdedx / bene * 1000)

top_dx = rxdx_table %>%
  filter(year==2011) %>%
  group_by(dx_cat) %>%
  summarize(max_cpkp=max(cpkp)) %>%
  mutate(over_10=max_cpkp >= 10) %>%
  arrange(desc(max_cpkp))

top_dx %>%
  kable(caption='Diagnoses by maximum drug usage in 2011')
```

```{r top_rxdx}
infection_sites = read_tsv('infection_sites.tsv')

top_dx %>%
  filter(over_10) %>%
  slice(-1) %>% # drop "remaining codes"
  select(dx_cat) %>%
  inner_join(rxdx_table, by='dx_cat') %>%
  left_join(infection_sites, by='dx_cat') %>%
  filter(year==2011) %>%
  group_by(site, antibiotic) %>%
  summarize(cpkp=sum(cpkp)) %>%
  arrange(site, desc(cpkp)) %>%
  group_by(site) %>%
  mutate(f=cpkp/sum(cpkp), cumf=cumsum(f)/sum(f)) %>%
  do(head(., 5)) %>%
  kable(caption='Top drugs by diagnosis in 2011')
```

```{r prescribing_practice}
rxdx_models = read_tsv('tables/new/rxdx_models.tsv')

format_p = function(p) if_else(p<0.0001, '<.0001', format(round(p, 4), digits=4, nsmall=4))

combined_table = rxdx_table %>%
  mutate(cpkp=round(n_pdedx / bene * 1000, 1)) %>%
  filter(year %in% c(2011, 2014)) %>%
  select(antibiotic, dx_cat, year, cpkp) %>%
  spread(year, cpkp) %>%
  right_join(rxdx_models, by=c('antibiotic', 'dx_cat')) %>%
  mutate_at(vars(estimate, lower_ci, upper_ci), est2pct) %>%
  mutate(change=sprintf('%.1f (%.1f -- %.1f)', estimate, lower_ci, upper_ci)) %>%
  mutate(d=pmax(estimate-lower_ci, upper_ci-estimate)) %>%
  mutate(change2=sprintf('%.1f ± %.1f', estimate, d)) %>%
  mutate(p.value=format_p(p_value)) %>%
  select(dx_cat, antibiotic, `2011`, `2014`, change2, p.value) %>%
  arrange(dx_cat, antibiotic)
```

@@

```{r respiratory}
rxdx_kable = function(abxs, dxs) {
  combined_table %>%
    filter(dx_cat %in% dxs, antibiotic %in% abxs) %>%
    mutate(dx_cat=factor(dx_cat, levels=dxs),
           antibiotic=factor(antibiotic, levels=abxs)) %>%
    arrange(dx_cat, antibiotic) %>%
    kable()
}

rxdx_kable(c('azithromycin', 'levofloxacin', 'amoxclav'),
           c('pneumonia', 'sinusitis', 'uri', 'bronchitis'))
```

@@

```{r claims_by_demography}
subpop_table = read_tsv('tables/new/claims_by_subpop.tsv') %>%
  mutate(cpkp=round(n_pde/n_bene*1000)) %>%
  filter(year %in% c(2011, 2014)) %>%
  select(subpop, year, cpkp) %>%
  spread(year, cpkp)

subpop_models = read_tsv('tables/new/subpop_models.tsv') %>%
  mutate_at(vars(estimate, lower_ci, upper_ci), est2pct) %>%
  mutate(pm=pmax(estimate-lower_ci, upper_ci-estimate)) %>%
  mutate(change=sprintf('%.1f (%.1f -- %.1f)', estimate, lower_ci, upper_ci)) %>%
  mutate(change2=sprintf('%.1f ± %.1f', estimate, pm)) %>%
  mutate(p.value=format_p(p_value)) %>%
  select(subpop, change2, p.value)

left_join(subpop_table, subpop_models, by='subpop') %>%
  kable(caption='Claims and trends by subpopulation')
```

@@

```{r other_respiratory}
rxdx_kable(c('azithromycin', 'levofloxacin', 'amoxclav'),
           c('pharyngitis', 'asthma', 'other_resp'))
```

## GI

```{r gi}
rxdx_kable(c('ciprofloxacin', 'metronidazole', 'levofloxacin'),
           c('gi', 'gi_t3'))
```

@@

```{r uti}
rxdx_kable(c('ciprofloxacin', 'tmpsmx', 'nitrofurantoin'),
           c('uti', 'uti_t3'))
```

@@

```{r ssti}
rxdx_kable(c('cephalexin', 'tmpsmx'),
           c('ssti', 'ssti_t3'))
```
